Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-05-31 ms.tex
some more notes on crosshatch as a function of location.

\subsubsection{Position of SubGrism Array}
\begin{figure}[!hbtp]
\centering
\includegraphics[width=0.99\columnwidth]{subg_pos_topGrism64.pdf}\\
\includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion.pdf}\\
\includegraphics[width=0.99\columnwidth]{subg_pos_grism64flat.pdf}\\
\vspace{0.2in}
\includegraphics[width=0.99\columnwidth]{subg_pos_topGrism64_psd.pdf}\\
\includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion_psd.pdf}\\
\includegraphics[width=0.99\columnwidth]{subg_pos_grism64_psd.pdf}\\
\caption{
The top of the array has the smallest level of crosshatching and the middle has the largest.
This is visible in the flat field images (top three panels) and their power spectral density functions (bottom three panels) for three different sections of the A5 detector: a theoretical ``aperture'' position at the top of the array, the full frame position near Y=512 and the nominal SUBGRISM64 at the bottom of the array.
 }\label{fig:subpixScanSimulation}
\end{figure}

>>>>

\subsubsection{Position of SubGrism Array}

The crosshatch pattern varies in amplitude and angular dependence from one physical location on the detector to another.
The ALONG detector has more pronounced crosshatching toward the middle of the detector that falls off toward the perimeter.
On the other hand, the BLONG detector has more pronounced crosshatching towards the boundary.
We fit the crosshatch pattern to three regions of the detector:
\begin{itemize}
	\item The 2048$\times$64 SUBGRISM64 nominal position at the bottom of the array. Bottom Left corner is (0,0)
	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector. Bottom Left corner is (0,1983)
	\item A 2048$\times$64 cutout of the full frame detector that is centered on the grism time series field point.
\end{itemize}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=0.99\columnwidth]{subg_pos_topGrism64.pdf}\\
\includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion.pdf}\\
\includegraphics[width=0.99\columnwidth]{subg_pos_grism64flat.pdf}\\
\vspace{0.2in}
\includegraphics[width=0.99\columnwidth]{subg_pos_topGrism64_psd.pdf}\\
\includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion_psd.pdf}\\
\includegraphics[width=0.99\columnwidth]{subg_pos_grism64_psd.pdf}\\
\caption{
The top of the array has the smallest level of crosshatching and the middle has the largest.
This is visible in the flat field images (top three panels) and their power spectral density functions (bottom three panels) for three different sections of the A5 detector: a theoretical ``aperture'' position at the top of the array, the full frame position near Y=512 and the nominal SUBGRISM64 at the bottom of the array.
 }\label{fig:subpixScanSimulation}
\end{figure}
